Consistent Polyhedral Surrogates via Embedding

### 2019-05-16 notes/jessie-proof-sketches.tex
Sketches ready for a pass over

Throughout this section, consider $F$ to be the facets of the projection of the surface of $\risk{L}$.
For a facet $f$, we also consider $u_f = \argmin_u L(u, p)$ for any $p \in \inter{f}$.
(We know that this $u_f$ is the same regardless of the choice of $p$ since $\risk{L}$ has a constant derivative on $\inter{f}$) \jessie{This implicitly assumes $\risk{L}$ is polyhedral, although this isn't stated in Prop 1.}

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}[Property version]
  For the forward implication, suppose $L$ embeds the discrete loss $\ell$.
  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma$ elicited by $\ell$.

@@

  For the reverse implication, see proof below.
  \jessie{I don't see a way that COLT results make this easier, since we don't talk about Bayes Risk that much.}
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
  %Jessie's first attempt at a proof
  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ contradicts the assertion that $L$ embeds $\ell$.

@@

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}[Property version]
  Suppose $\Gamma := \prop{L}$ embeds the finite property $\gamma$, elicited by the discrete loss $\ell$.
  We know that $\risk{\ell}$ is polyhedral as $\gamma$ is finite.
  Since $L$ embeds $\ell$, we know $\risk{L} = \risk{\ell}$, and therefore $\risk{L}$ is also polyhedral. 
  \jessie{This direction is shorter below without properties.}

  Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
  For the set of facets $F$ projected from the surface of $\risk{L}$, construct $\R := \{u_f\}_{f \in F}$, with $u_f$ as described earlier. 
  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\gamma := \Gamma \cap \R$ elicited by the discrete loss $\ell := L|_\R$. 
  Thus, $L$ embeds $\ell$.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral.
  Therefore, $\risk{L}$ is polyhedral.

@@

  \raf{Just take the discrete reports to be the facets, and use the Bayes risk result.}
\end{proof}

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
\begin{proof}[Non-property version]
  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
  \jessie{$L(u,p)$ polyhedral in $\reals^d$ for all $p \in \simplex$ implies $L^*(0,p) = -\risk{L}(p)$ polyhedral in $\simplex$ implies $\risk{L}$ polyhedral.
  Now we can apply Proposition~\ref{prop:embed-risk-poly} to observe the result.}
\end{proof}
\hrulefill
\begin{proof}[Property version]
  We know $L$ polyhedral implies $\risk{L}$ is polyhedral. \jessie{Does the above argument not work?  If it does, the other proof is shorter anyways.}
  As before, construct, $\R = \{u_f\}_{f \in F}$, which is finite, as $F$ is finite. \jessie{We need the above statement to know that $F$ is finite, and therefore $\ell$ is discrete.}
  To see our result, we specifically show that $L$ embeds $L|_\R$.

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}[Property version]
  Consider $\gamma := \prop{\ell}$, which is a finite property as $\dom(\ell)$ is finite.
  The result is a corollary of \jessie{COLT Theorem 35} Theorem~\ref{thm:general-duality-embedding}, where the polyhedral loss $L$ is as constructed in the proof.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
  It is sufficient to show the existence of a polyhedral loss $L$ such that $\risk{\ell} = \risk{L}$.
  Consider that $\risk{\ell}$ is closed and concave, since the domain $\simplex$ is closed.
  Now construct $L$ as in \jessie{DKR} Duchi et al.~\cite[Proposition 3]{duchi2010multiclass}, where $H = \risk{\ell}$.
  Then we know that $\risk{L} = \risk{\ell}$ by their result, and thus $L$ embeds $\ell$.
  Moreover, we can see that $L$ is polyhedral as it is a linear transformation of a polyhedral concave function $\risk{\ell}$.
\end{proof}

\begin{corollary}\label{cor:finite-elicit-embed}
  Let $\gamma$ be a finite property.
  The following are equivalent.
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\gamma$ is elicitable.
  \item $\gamma$ is embeddable.
  \item $\gamma$ is embeddable via a polyhedral loss.
  \end{enumerate}
\end{corollary}
\begin{proof}[Property version]
	We just need to show that $2 \implies 1$.
	Consider the finite property $\gamma$ embedded by the discrete loss $\ell$. \jessie{Need a proof that $\ell$ is discrete?}
	By Theorem~\ref{thm:discrete-loss-poly-embeddable}, we know that there is a polyhedral loss $L$ that embeds $\ell$.
	Therefore, $\Gamma := \prop{L}$ embeds $\gamma$.
	Since $L$ elicits $\Gamma$, we can then see that $L|_\R$ elicits $\gamma$ by \jessie{COLT Lemma 11... hold up.  We need something else here.  This statement isn't quite true.}.
	Thus, $\gamma$ is elicitable.
	\jessie{This seems like a lot of running in circles, and it's not quite right.}
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  We trivially have $3\Rightarrow 2$.
  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
  Finally, to see $2\Rightarrow 1$,
  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary... let's see if it follows more directly from the above.  If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
\end{proof}

>>>>

Throughout this section, consider $F$ to be the facets of the projection of the surface of $\risk{\ell}$.
For a facet $f$, we also consider $u_f = \argmin_u L(u, p)$ for any $p \in \inter{f}$.
(We know that this $u_f$ is the same regardless of the choice of $p$ since $\risk{\ell}$ has a constant derivative on $\inter{f}$) 
\hrule
\hrulefill
\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  \jessie{Ready for a look over.}
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}[Property version]
  For the forward implication, suppose $L$ embeds the discrete loss $\ell$.
  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma$ elicited by $\ell$.

@@

  For the reverse implication, we use contradiction. \jessie{But no properties... I didn't see how.  Different technique from below though.}

  First, assume that $\risk{\ell} \neq \risk{L} +c$ for any constant $c$.
  Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$ \jessie{define}, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}$.
  Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.

  Now, if $\risk{\ell} = \risk{L}+c$ for some constant $c \neq 0$, then we contradict part $(i)$ of the definition of embedding where the loss values must match up.

  Therefore, if the loss $L$ embeds the discrete loss $\ell$, then we must observe $\risk{L} = \risk{\ell}$.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
  %Jessie's first attempt at a proof
  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ contradicts the assertion that $L$ embeds $\ell$.

@@

\hrule
\hrulefill

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
  \jessie{Ready for a look over.}
\end{proposition}
\begin{proof}[Property version]
  Suppose $\Gamma := \prop{L}$ embeds the finite property $\gamma$, elicited by the discrete loss $\ell$.
  We know that $\risk{\ell}$ is polyhedral as $\gamma$ is finite.
  Since $L$ embeds $\ell$, we know $\risk{L} = \risk{\ell}$, and therefore $\risk{L}$ is also polyhedral. 
  \jessie{This direction is shorter below without properties.}

  Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
  For the set of facets $F$ projected from the surface of $\risk{L}$ (cells of $P_L$), construct $\R := \{u_f\}_{f \in F}$, with $u_f$ as described earlier. 
  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\gamma := \Gamma \cap \R$ elicited by the discrete loss $L|_\R$. 
  Thus, $L$ embeds a discrete loss-- namely, $L|_\R$.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral.
  Therefore, $\risk{L}$ is polyhedral.

@@

  \raf{Just take the discrete reports to be the facets, and use the Bayes risk result.}
\end{proof}
\hrule 
\hrulefill

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
  \jessie{My thoughts are in a comment, and I think Raf said it was wrong at one point, but I don't understand why exactly.}
\end{theorem}
\jessie{Non-property version is simpler.}
\begin{proof}[Non-property version]
  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
  \jessie{$L(u,p)$ polyhedral in $\reals^d$ for all $p \in \simplex$ implies $L^*(0,p) = -\risk{L}(p)$ polyhedral in $\simplex$ implies $\risk{L}$ polyhedral.
  Now we can apply Proposition~\ref{prop:embed-risk-poly} to observe the result.}

  \jessie{Attempt 2: Since $L$ is polyhedral, it is the pointwise max of a finite set of affine functions.  As $\risk{L}$ is defined as the inf over a finite set of polyhedral functions, its epigraph is a subset of the expected loss for each report, and thus is still the finite intersection of closed halfspaces.}
  \jessie{Going to refresh my brain-- come back to this, but if the other proof is insufficient, this idea is chasing down the correct path.}
\end{proof}
\hrulefill
\begin{proof}[Property version]
  We know $L$ polyhedral implies $\risk{L}$ is polyhedral. \jessie{Does the above argument not work?  If it does, the other proof is shorter anyways.}
  As before, construct, $\R = \{u_f\}_{f \in F}$, which is finite, as $F$ is finite. \jessie{We need the above statement to know that $F$ is finite, and therefore $\ell$ is discrete.}
  To see our result, we specifically show that $L$ embeds $L|_\R$.

@@

\hrule
\hrulefill

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
  \jessie{Ready for a look over.}
\end{theorem}
\begin{proof}[Property version]
  Consider $\gamma := \prop{\ell}$, which is a finite property as $\dom(\ell)$ is finite.
  The result is a corollary of \jessie{COLT Theorem 35} Theorem~\ref{thm:general-duality-embedding}, where the polyhedral loss $L$ is as constructed in the proof.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
  It is sufficient to show the existence of a polyhedral loss $L$ such that $\risk{\ell} = \risk{L}$.
  Consider that $\risk{\ell}$ is closed and concave, since the domain $\simplex$ is closed.
  Now construct $L$ as in \jessie{DKR} Duchi et al.~\cite[Proposition 3]{duchi2010multiclass}, where $H = \risk{\ell}$.
  Then we know that $\risk{L} = \risk{\ell}$ by their result, and thus $L$ embeds $\ell$ by Proposition~\ref{prop:embed-bayes-risks}.
  Moreover, we can see that $L$ is polyhedral as it is a linear transformation of a polyhedral concave function $\risk{\ell}$.
\end{proof}

\hrule
\hrulefill

\begin{corollary}\label{cor:finite-elicit-embed}
  Let $\gamma$ be a finite property.
  The following are equivalent.
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\gamma$ is elicitable.
  \item $\gamma$ is embeddable.
  \item $\gamma$ is embeddable via a polyhedral loss.
  \end{enumerate}
  \jessie{Not happy with this, but not sure how to improve it.}
\end{corollary}
\begin{proof}[Property version]
	We just need to show that $2 \implies 1$.
	Consider the finite property $\gamma$ embedded by the discrete loss $\ell$. \jessie{Need a proof that $\ell$ is discrete?}
	By Theorem~\ref{thm:discrete-loss-poly-embeddable}, we know that there is a polyhedral loss $L$ that embeds $\ell$.
	Therefore, $\Gamma := \prop{L}$ embeds $\gamma$.
	Since $L$ elicits $\Gamma$, we can then see that $L|_\R$ elicits $\gamma' := \Gamma \cap \R$ by \jessie{COLT Lemma 11... hold up.  We need something else here.  This statement isn't quite true.}.
	Thus, $\gamma$ is elicitable by some relabeling of $L|_\R$.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  We trivially have $3\Rightarrow 2$.
  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
  Finally, to see $2\Rightarrow 1$,
  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary... let's see if it follows more directly from the above.  If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
\end{proof}
